---
title: "Final Project"
Name: "Sulman Mohamed"
output:
  html_document:
    df_print: paged
---


```{r}
library(tidyverse)
library(ggplot2)
library(readxl)
library(dplyr)
```

### Load all Comicbook Movies Ever Made
```{r}
comicmovie <- read_excel("comicmovie.xlsx")
comicmovie
nrow(comicmovie)
```

```{r}
glimpse(comicmovie)
```

# Group Data

### All Marvel Movies
```{r}
Marvel <- filter(comicmovie, Owner == "Marvel") 
  nrow(Marvel)
  
Marvel
```
```{r}
Marvel_Budget <-summarise(Marvel, ave_budget = mean(Budget, na.rm=TRUE))
Marvel_Budget
```


### All DC Movies
```{r}
DC <- filter(comicmovie, Owner == "DC")
nrow(DC)
DC
```
```{r}
DC_Budget <- summarise(DC, ave_budget = mean(Budget, na.rm=TRUE))
DC_Budget
```

### All movies not made by DC or Mavel
```{r}
Other <- filter(comicmovie, Owner == "Other")
nrow(Other)
Other
```
```{r}
Other_Budget <- summarise(Other, ave_budget = mean(Budget, na.rm=TRUE))
Other_Budget
```





## Most Expensive and Cheapest Comic Movie of All Time
```{r}
filter(comicmovie, Budget == max(Budget, na.rm = TRUE))

filter(comicmovie, Budget == min(Budget, na.rm = TRUE))
```




### Group movies by Ratings

#### T1 = Good Movie
#### T2 = Average Movie
#### T3 = Bad Movie
```{r}
Good_Movies <- filter(comicmovie, IMDB >= 7)
arrange(Good_Movies, desc(IMDB))

Good_Marvel <- filter(Good_Movies, Owner=="Marvel")
Good_DC <- filter(Good_Movies, Owner=="DC")
Good_Other <- filter(Good_Movies, Owner=="Other")

Average_Movies <- filter(comicmovie, IMDB >= 6, IMDB < 7)
Average_Movies
Average_Marvel <- filter(Average_Movies, Owner=="Marvel")
Average_DC <- filter(Average_Movies, Owner=="DC")
Average_Other <- filter(Average_Movies, Owner=="Other")

Bad_Movies <- filter(comicmovie, IMDB < 6,  )
Bad_Movies
Bad_Marvel <- filter(Bad_Movies, Owner=="Marvel")
Bad_DC <- filter(Bad_Movies, Owner=="DC")
Bad_Other <- filter(Bad_Movies, Owner=="Other")
```

## Analysis
#### num of Good Movies

```{r}
nrow(Good_Marvel)
nrow(Good_DC)
nrow(Good_Other)
```



#### num ofAverage Movies

```{r}
nrow(Average_Marvel)
nrow(Average_DC)
nrow(Average_Other)
```


#### num of Bad Movies
```{r}
nrow(Bad_Marvel)
nrow(Bad_DC)
nrow(Bad_Other)
```

#### Top 10 most Expensive Comic Movies
```{r}
Expensive <-arrange(comicmovie, desc(Budget))
head(Expensive, 10)
```

#### Top 10 Cheapest Comic Movies
```{r}
Cheap <-arrange(comicmovie, Budget)
head(Cheap, 10)
```

## Budget Comparison
```{r}
Owner_ <- c("Marvel", "DC", "Other")
ave_Budget <- c(135209145, 112690080, 80250000)
num_of_Good_Movies <- c(33, 12, 1)
num_of_Average_Movies <- c(19, 7, 1)
num_of_Bad_Movies <- c(18, 16, 2)
  
df <- data.frame(Owner_, ave_Budget,num_of_Good_Movies, num_of_Average_Movies, num_of_Bad_Movies)

print (df)
```

## Visual Data


### Year with the most movies
```{r}
comicmovie %>%  
ggplot(aes(x=Year)) +
    geom_density(fill="#69b3a2", color="#e9ecef", alpha=1)
```
```{r}
most_year<-filter(comicmovie, Year == "2019")
nrow(most_year)
```




### Comparing Brands Budget


```{r}
ggplot(data = df) + 
  geom_col(aes(x = Owner_ , y = ave_Budget, fill = Owner_)) 
```



### Comparing Number of Good Movies
```{r}
ggplot(data = df) + 
  geom_col(aes(x = Owner_ , y = num_of_Good_Movies, fill = Owner_)) 
```

### Comparing Number of Average Movies
```{r}
ggplot(data = df) + 
  geom_col(aes(x = Owner_ , y = num_of_Average_Movies, fill = Owner_)) 
```

### Comparing Number of Bad Movies

```{r}
ggplot(data = df) + 
  geom_col(aes(x = Owner_ , y = num_of_Bad_Movies, fill = Owner_)) 
```



```{r}
ggplot(data = comicmovie) + 
  geom_point(aes(x = Budget, y = IMDB, color = Owner))
```
### Movies with very diffrent audiance and Rotten Tomatoe scores 
```{r}
RTvsA<- mutate(comicmovie, RT_vs_Audiance = (Audience/RT))

dif <- arrange(RTvsA, desc(RT_vs_Audiance))
head(dif, 3)
```














